Gesture Typing on Virtual Tabletop: Effect of Input Dimensions on Performance

### 2017-08-28 paper.tex
copyright, keywords

%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
\copyrightinfo{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org. \\
{\emph{ISS '17}}, October 17--20, 2017, Brighton, United Kingdom. \\
Copyright \copyright~2017 ACM ISBN 978-1-4503-4691-7/17/10. \\
10.1145/3132272.3135074}
%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)

% \CopyrightYear{2017}
% \setcopyright{rightsretained}
% \conferenceinfo{ISS '17}{October 17--20, 2017, Brighton, United Kingdom}\isbn{978-1-4503-4691-7/17/10}
% \doi{https://doi.org/10.1145/3132272.3135074}

@@

% Paper metadata (use plain text, for PDF inclusion and later re-using, if desired)
\def\plaintitle{Gesture Typing on Virtual Surfaces: Effect of Input Dimensions on Performance}
\def\plainauthor{Name}
\def\plainkeywords{Indirect Interaction, Gesture Input, Gesture Keyboard, Mobile, Continuous Interaction, Tabletop, Text Input}
\def\plaingeneralterms{Documentation, Standardization}

@@

\category{H.5.m}{Information interfaces and presentation (e.g., HCI)}{Miscellaneous}.
%See \cite{ACMCCS}
% See: \url{http://www.acm.org/about/class/1998/}
% for help using the ACM Classification system.
% \textcolor{red}{Optional section to be included in your final version, but strongly encouraged.}

>>>>

%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
\copyrightinfo{Permission to make digital or hard copies of part or all of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for third-party components of this work must be honored. For all other uses, contact the Owner/Author. \\
{\emph{ISS '17}}, October 17–20, 2017, Brighton, United Kingdom. \\
\copyright~2017 Copyright is held by the owner/author(s). \\
ACM ISBN 978-1-4503-4691-7/17/10. \\
https://doi.org/10.1145/3132272.3135074}
%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)

@@

% Paper metadata (use plain text, for PDF inclusion and later re-using, if desired)
\def\plaintitle{Gesture Typing on Virtual Surfaces: Effect of Input Dimensions on Performance}
\def\plainauthor{Antoine Loriette}
\def\plainkeywords{Indirect Interaction; Gesture Input; Gesture Keyboard; Mobile; Continuous Interaction; Tabletop; Text Input}
\def\plaingeneralterms{}

@@

\category{H.5.2}{Information interfaces and presentation (e.g. HCI)}{User Interfaces}.
%See \cite{ACMCCS}
% See: \url{http://www.acm.org/about/class/1998/}
% for help using the ACM Classification system.
% \textcolor{red}{Optional section to be included in your final version, but strongly encouraged.}
